---
title: "Exercise B Week 1"
format: html
editor: visual
---

## Exercise B Week 1

#### What to do: 

Create an HTML document with R code that samples 100 values from a negative binomial distribution (say, mu=10, dispersion=2; using the parameterisation with mean=mu and variance=mu+mu2\*dispersion); create a histogram of sampled data on both the linear and log \[or maybe log(x+1) due to zeros\] scale; Write 1-2 sentences to describe your steps (ideally also with section headings) and report the mean and variance of the sample in line in the text.

#### 1.) load libraries and set seed

We need the library MASS for the function "rnegbin" (see below). At first, i thought I was going to work with the function "rnbinom" and for that, I would have used the library stats. To make the process replicable, I set the seed.

```{r}
library(MASS)
#library(stats)
set.seed(41)
```

#### 2.) create data

It turns out that rnbinom is not the correct function when we want to work with the variance mu+mu^2^/theta. The correct function is rnegbin, where we can generate 100 random outcomes from a Negative Binomial distribution with mean mu=10 and theta=2 with the variance that is asked for.

```{r}
#?rnbinom
#data <- rnbinom(100, size=2, mu=10)
#?rnegbin
data <- rnegbin(100, mu=10, theta=2)
```

#### 4.) Plot the histograms

Lastly, I created one histogram on the linear scale (with a title so it is obvious that it is linear) and one on the log scale. In order to avoid computation errors if we have a 0 in the data, I took the logarithm of the data + 1.

```{r}
#?hist
hist(data, main="Histogram on the linear scale")
hist(log(data+1), main="Histogram on the log scale")
```

The mean of the data is given by mu=`r mean(data)` and the variance is var=`r var(data)`.
